```{r event_counts, echo = FALSE, warning = FALSE, message = FALSE}
# Figure out what we've got in the way of events so we 
# can conditionally update the sections in the report.
evt_ttl <- df_events %>% nrow()
evt_no_data_ttl <- df_events %>% filter(assessment == "No Data") %>% nrow()
evt_minimal_data_ttl <- df_events %>% filter(assessment == "Minimal Data") %>% nrow()
```

`r if(evt_ttl == 0) "There are no events enabled in the report suite."`

`r if(evt_no_data_ttl != 0) "### Events with No Data"`

`r if(evt_no_data_ttl != 0) "The following events have **no data** for the report period:"`

```{r events_no_data, echo = FALSE, warning = FALSE, message = FALSE}
if(evt_no_data_ttl != 0){
  df_events %>% filter(assessment == "No Data") %>% 
    mutate(description = ifelse(is.na(description), "\\-", description)) %>% 
    select(id, name, description, type) %>% 
    kable(col.names = c("event", "Name", "Description", "Type")) %>% 
    kable_styling(bootstrap_options = c("striped", "condensed")) %>% 
    column_spec(1, width = "8em") %>% 
    column_spec(2, width = "12em")  %>% 
    column_spec(4, width = "6em") 
}
```

`r if(evt_minimal_data_ttl != 0) "### Events with Minimal Data"`

`r if(evt_minimal_data_ttl != 0) paste("The following events have **minimal data** for the report period, defined as having a total value below", format(min_instances, big.mark = ",", trim = TRUE), "in the assessed timeframe:")`

```{r events_minimal_data, echo = FALSE, warning = FALSE, message = FALSE}
if(evt_minimal_data_ttl != 0){
  df_events %>% filter(assessment == "Minimal Data") %>% 
    mutate(event_total = format(event_total, big.mark = ",", trim = TRUE)) %>% 
    mutate(description = ifelse(is.na(description), "\\-", description)) %>% 
    select(id, name, description, type, event_total) %>% 
    kable(col.names = c("event", "Name", "Description", "Type", "Event Total")) %>% 
    kable_styling(bootstrap_options = c("striped", "condensed")) %>% 
    column_spec(1, width = "8em") %>% 
    column_spec(2, width = "12em") %>% 
    column_spec(4, width = "6em") %>% 
    column_spec(2, width = "8em") 
}
```

`r if(evt_ttl != 0 & evt_ttl != evt_no_data_ttl) "### Event Trends"`

`r if(evt_ttl != 0 & evt_ttl != evt_no_data_ttl) "Below is a daily trend plot for each event that has any data:"`

```{r event_trends, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 6, fig.height = 3}

if(evt_ttl != 0 & evt_ttl != evt_no_data_ttl){
  
  # Function to generate a plot of daily date for a given event_id
  get_event_daily_trend <- function(event_id, prefix = ""){
    
    # Main df for the line
    df <- df_events_daily %>% 
      filter(id == event_id)
    
    gg <- ggplot(df, aes(x = day, y = value, group = 1)) + 
      geom_line(color = "#009CAB") +
      scale_y_continuous(labels = comma, expand = c(0,0), limits = c(0, max(df$value) * 1.05)) +
      labs(title = paste0(prefix, event_id, ": ", df$name[[1]]),
           subtitle = "Event Total by Day",
           caption = paste("Source: Adobe Analytics. Report Suite:", rsid, "-", start_date, "to", end_date)) +
      theme_minimal() +
      theme(plot.title.position = "plot",
            plot.subtitle = element_text(color = "gray40"),
            plot.caption = element_text(color = "gray40", face = "italic"),
            axis.title = element_blank(),
            axis.line.x = element_line(color = "gray60"),
            panel.grid.minor.x = element_blank(),
            legend.position = "top",
            legend.title = element_blank(),
            legend.text = element_text(size = 11, color = "gray20"))
    
    print(gg)
  }
  
  # Generate a plot for every event that has data
  df_events %>% filter(assessment != "No Data") %>% pull(id) %>% walk(get_event_daily_trend)
  
}

```
